\documentclass{article}
\usepackage{tabularx}
\usepackage{booktabs}
\begin{document}

\section*{Meeting Notes}

\textbf{Date:} \today \\
\textbf{Time:} 2:00pm - 4:00pm \\
\textbf{Location:} Zoom Meeting \\
\textbf{Attendees:} John Smith, Jane Doe, Michael Johnson, Emily Davis \\

\bigskip

\textbf{Agenda}

\begin{tabularx}{\textwidth}{X}
\toprule
1. Review of previous meeting minutes \\
2. Update on project progress \\
3. Discussion on budget concerns \\
4. Any other business \\
\bottomrule
\end{tabularx}

\bigskip

\textbf{Discussion}

\begin{itemize}
    \item Review of previous meeting minutes - John Smith provided an overview of the key points discussed during the last meeting and any action items that were assigned.
    \item Update on project progress - Jane Doe provided an update on the progress of the project, highlighting any challenges faced and the steps taken to address them.
    \item Discussion on budget concerns - Michael Johnson presented the current budget situation and discussed potential options for addressing any concerns.
    \item Any other business - Emily Davis brought up any other relevant topics that were not covered in the agenda.
\end{itemize}

\textbf{Action Items}

\begin{itemize}
    \item John Smith to follow up on action item 1 from the previous meeting.
    \item Jane Doe to provide a detailed update on the project progress for the next meeting.
    \item Michael Johnson to present a proposal for addressing budget concerns at the next meeting.
    \item Emily Davis to schedule the next meeting for two weeks from now.
\end{itemize}

\end{document}
